Identifying regime transitions for water governance at a basin scale

### 2023-05-09 paper/letter/response_letter/AR_to_RC/response_letter.tex

\begin{figure}[!htb]
	\centering
	\includegraphics[width=\textwidth]{sup/sf_measured_runoff.jpg}
	\caption{绘图测试}\label{fig:xfig0}
\end{figure}

% 我们强调流域治理需要考虑这些因素，但我们可能很难穷尽优秀的流域治理策略需要考虑哪些因素。因此，IWGI至少让我们可以知道在诸多治理因素的共同影响下，流域的未来正在走向何方。
\AR*{}

\subsection{Major concern \#2}
% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
\RC{} The results are summative. I would suggest providing more information on the results of the three indices and the IWGI.\ For example, the results of the three indices, and the results for the sub-regions. And please explain the range of the three indicators, IS, IP, IA, and the IWGI, and the meanings of different values. These details could help readers understand the reasonability of the results.

% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
% 再方法中补充了指标的取值范围（三个子指标的变化范围都是0～1）。
\AR{} Thanks for point it out! Now

\AR*{} Figure SX to SX are three indicators changing trends with different regions' contribution.

\AR*{} Ranges of three indicators and meaning of their values are further explained in the methodology section, now:

\begin{quote}[page=1, sline=1]
	Methods
\end{quote}

@@

\subsection{Major concern \#3}
% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
\RC{} The data used in this study seem to have different time periods, and most data are from before 2013. The hydrological regime and water governance in the Yellow River should have changed significantly in the recent decade. Therefore, incorporating the result from the recent decade would make this study more solid.

\AR{} Multiple-source dataset.

\subsection{Major concern \#4}
% 这三个指标之间可能存在相互作用/相互联系。作者是否检查了指标之间的关系?
\RC{} There might be interactions/interconnections among the three indicators. Did the authors examine the relations between the indicators?

\AR{} Yes, we did examination for the interconnections between the three indicators. Sorry we didn't make the information accessible. Now, we added a table to describe them:

\begin{quote}
	Table
\end{quote}

\AR*{} Note that independent is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
However, our

@@

\subsection{Major concern \#5}
% IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。
\RC{} The IWGI includes reservoir storage information in the "stress" aspect. However, the water conveyance ability is not represented, which is also an important indicator of water governance/hydrosocial resilience.

% 短期的输水能力是衡量水治理/水社会复原力的重要指标
% 但年尺度上，变化不大
\AR*{} Correct, conveyance is crucial to water governance/water society resilience, especially in the short term. However, the IWGI in this study focuses on annual time resolution. At this scale, conveyance has a less significant impact on water governance. From this point of view, we have two reasons that IWGI doesn't have to consider this in our study:

% 我们检验过了年尺度的输水数据，基本变化不大

% 水治理很复杂，考虑到越来越多的要素会增加其复杂度。Scarcity是本研究使用最复杂的指标，因为这是一个经过检验的，可以有效表征的指数。如果经过检验影响不大，没有必要增加复杂度。

@@

\subsection{Major concern \#6}
% 我建议在标题中加上“黄河流域”。因为没有对IWGI的适用性和有效性进行测试或讨论。它能在其他盆地使用吗?使用索引的先决条件是什么?
\RC{} I would suggest adding "Yellow River basin" in the title. Because the applicability and validity of the IWGI were not tested or discussed. Can it be used in other basins? What is the prerequisite for using the index?

% 感谢你的提议，我们增加了黄河流域

% 关于IWGI的泛用性，实际上我们在讨论中讨论了这一点。我们也

% 我们如今在方法部分提到了使用它的先决条件。

\subsection{Major concern \#7}
% 最好在引言部分解释“水治理机制”的概念，然后解释使用综合指数IWGI代表水治理机制的必要性。
\RC{} It would be better to explain the concept "water governance regime" in Introduction and then explain the necessity of using the integrated index IWGI for representing the water governance regime.

% 感谢你的建议，我们做了如下解释：
\begin{quote}
	``Water governance regime'' is \ldots
\end{quote}

\subsection{Detailed issues}

### 2023-05-09 paper/main/01_introduction.tex
style(paper): :lipstick: fix all chktex warns

\label{Intro.}
Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being
\cite{gleeson2020a,gleeson2020b}.
As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water
\cite{ahlstrom2021,biermann2012,steffen2020}.
Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers
\cite{sivapalan2012,qin2014,abbott2019}.
Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance
\cite{best2019,dibaldassarre2019}.

Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacility2016}.
% 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。
Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used. % todo cite OECD
From the water side, intuitive indexes can provide an embodiment of governance outcomes.
Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.

An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress
\cite{qin2019,wada2014,huang2021}.
Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)
\cite{liu2017,florke2018,jaeger2019}.
Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations
\cite{schmandt2021,speed2013}.
Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.

A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it \cite{kjellen2015, grafton2013}.
Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions
\cite{falkenmark2021,bressers2013,loch2020}.
For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
However, the lack of a comprehensive but straightforward approach to identifying changes in water governance regimes represents a challenge for efforts to enhance the sustainability of water resource use.
Filling this gap, which is the aim of this paper, is essential for the appropriate alignment of human and water systems.

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI). Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}). Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance. For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
	}
	\label{fig:framework}
\end{figure*}

The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history
\cite{mostern2021,best2019}.
Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads
\cite{wang2016e,song2020a}.
However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic
\cite{wang2019c}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors
\cite{wohlfart2016a}.
Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide \cite{nickum2021}.
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

>>>>

Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being~\cite{gleeson2020a,gleeson2020b}.
As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014,abbott2019}.
Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.

Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water~\cite{oecd2018, wang2017}, essentially about ``who gets water, when and how''\cite{lasswell2018}.
Therefore, the United Nations Development Programme (UNDP) has suggested that three core aspects of water use decided by water governance correspondingly: ``When and what water to use?'' (stress), ``How does water provide different services for human well-being?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)~\cite{undpwatergovernancefacility2016}.
% 为充分考虑这些人类活动影响，做出有助于水治理实践的评估，以往的综合指标主要可分成两类：评估水系统与评估治理系统。
Responding the questions for better water governance practices, previous studies can divide into two categories of comprehensive indicators by focusing on water systems or governance systems.
From the governance side, an integrated index can explicitly denote what practices are effecting water governance.
However, a comprehensive and detailed list of the key components for assessment of water governance is rare, hence quantitative studies usually propose indexes by using proxy dataset of human activities as a simpler way~\cite{varis2019}.
A qualitative approach to the assessment of water governance can list more elements regarding to water governance, where OECD's index and assessment dataset are the most widely used. % todo cite OECD
From the water side, intuitive indexes can provide an embodiment of governance outcomes.
Water stress is the most widely concerned aspect, which has been far developed in comprehensive index when incorporating human's regulation step by step.
As instances, traditional water stress index only demands and supply, water scarcity index by involving accessibility, and SFV-index further integrated flexibility.
These easy-to-use indexes of water stress, however, seem to have difficulty in providing a comprehensive characterization of the above water governance aspects without concerning its social usage (i.e., water use purpose and water allocation).
Standing from water side for comprehensively quantify governance outcomes, here we aim to develop an integrated water governance index to identify its changes by involving apportions of water uses between regions and sectors.

An important reason for developing this new index is practices of water governance changes throughout development under a hybrid of social and natural drivers.
First, besides climate change impacts embedded in current water yield concerns, water stress is also tightly related to an increasingly insatiable demands from economic activities, while developing water storage to release the stress~\cite{qin2019,wada2014,huang2021}.
Second, the purpose of how water services human well-being is tilting the trade-offs between provisioning uses (e.g., drinking and food production) and non-provisioning uses (e.g., energy production)~\cite{liu2017,florke2018,jaeger2019}.
Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by growing systematic regulations~\cite{schmandt2021,speed2013}.
Since the transition to a human-dominated regime induced substantive changes in the three interwind aspects (stress, purpose, and allocation), considering them seperately can lead to systematic failure in water governance.

A first critical step in understanding the successes and failures of water governance is to identify the different regimes that underpin it~\cite{kjellen2015, grafton2013}.
Regimes of water governance arise within linked human-water systems (based on management, institutions, and exploitation) to create local equilibria in social-ecological structures and functions~\cite{falkenmark2021,bressers2013,loch2020}.
For example, under a human-dominated regime, reservoirs make water stress easier to be alleviated because of flexibility; growing energy and industrial demands make water services purposes lopsided to non-provisioning sectors; conveyance systems make water allocation more planned (Figure~\ref{fig:framework}~A)
However, the lack of a comprehensive but straightforward approach to identifying changes in water governance regimes represents a challenge for efforts to enhance the sustainability of water resource use.
Filling this gap, which is the aim of this paper, is essential for the appropriate alignment of human and water systems.

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI). Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}). Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance. For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
	}\label{fig:framework}
\end{figure*}

The Yellow River Basin (YRB), which contains the fifth-largest and most sediment-rich river in the world, needs integrated water governance because of geological and human history~\cite{mostern2021,best2019}.
Since the 1960s, governance practices such as reservoirs, levees, and conservation measures have contained the issues troubled by thousands of years of high sediment loads~\cite{wang2016e,song2020a}.
However, new challenges such as decreased streamflows and water depletions occurred in more recent times, leading to water use regulation and water transfer across basins -different focused water governance tactic~\cite{wang2019c}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB to the satisfaction of all actors~\cite{wohlfart2016a}.
Governance challenges induced by environmental, economic, social, and political factors have resulted in YRB being among the most intensively-governed large river basins worldwide~\cite{nickum2021}.
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

### 2023-05-09 paper/main/02_methods.tex
style(paper): :lipstick: fix all chktex warns

@@

	We selected an indicator ($I_x$, $x=S$, $P$, or $A$, corresponding to stress, purpose, and allocation, respectively) to quantify the aspects effectively. Then, the above equation was transformed into a natural logarithm to facilitate calculation:
	\begin{equation}
		Transformation \propto ln(I_S) + ln(I_P) + ln(I_A)
	\end{equation}

@@

	where:
	\begin{equation}
		I'_x = (I_x - I_{x, min}) / (I_{x, max} - I_{x, min})
	\end{equation}

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress \cite{qin2019}. This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity. Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}). For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

@@

	\begin{equation}
		I_A = CEM = \sum_{i=1}^N -log(p_{i}) * p_{i}
	\end{equation}

@@

	\subsection{Change points detection}
		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
        \cite{pettitt1979}.
		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}}$ and $x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$. To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:

@@

		The most probable change point $\tau$ is found where its value satisfies $K_{\tau} = max|U_{t, T}|$ and the significance probability associated with value $K_{\tau}$ is approximately evaluated as:
		\begin{equation}
			p=2 \exp \left(\frac{-6 K_{\tau}^{2}}{T^{2}+T^{3}}\right)
		\end{equation}
		Given a certain significance level $\alpha$, if $p < \alpha$, we reject the null hypothesis and conclude that $x_{\tau}$ is a significant change point at level $\alpha$.

>>>>

% chktex-file 46

@@

	We selected an indicator ($I_x$, $x=S$, $P$, or $A$, corresponding to stress, purpose, and allocation, respectively) to quantify the aspects effectively. Then, the above equation was transformed into a natural logarithm to facilitate calculation:
	\begin{equation}
		Transformation \propto \ln(I_S) + \ln(I_P) + \ln(I_A)
	\end{equation}

@@

	where:
	\begin{equation}
		I'_x = (I_x - I_{x, \min}) / (I_{x, \max} - I_{x, \min})
	\end{equation}

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., (2019) to evaluate water stress~\cite{qin2019}. This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity. Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}). For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

@@

	\begin{equation}
		I_A = CEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
	\end{equation}

@@

	\subsection{Change points detection}
		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data~\cite{pettitt1979}.
		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}}$ and $x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$. To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:

@@

		The most probable change point $\tau$ is found where its value satisfies $K_{\tau} = \max|U_{t, T}|$ and the significance probability associated with value $K_{\tau}$ is approximately evaluated as:
		\begin{equation}
			p=2 \exp \left(\frac{-6 K_{\tau}^{2}}{T^{2}+T^{3}}\right)
		\end{equation}
		Given a certain significance level $\alpha$, if $p < \alpha$, we reject the null hypothesis and conclude that $x_{\tau}$ is a significant change point at level $\alpha$.

### 2023-05-09 paper/main/03_results.tex
style(paper): :lipstick: fix all chktex warns

\subsection{Water governance regimes}
\label{Res.1}

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/index.jpg}
	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: 1965-1978, P2: 1979-2001, and P3: 2002-2013.
	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
	\textbf{B,} correlation of trends between the IWGI and the indicators.
	\textbf{C,} across three indicators, changing components of the IWGI, whose directions shifts between different regimes.
	}
	\label{fig:IWGI}
\end{figure*}

% 这一节主要展示IWGI的变化趋势和WUR的划分
Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
% 第二阶段
In the second period (P2, 1979-2001), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
% 第三阶段
During the third period (P3, 1995-2013), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
% Overall
Taken together, the overall features of the three aspects in different periods are relative to a directional change in the combination of three aspects (Figure~\ref{fig:IWGI}C).

\subsection{Causes of the regime shifts}
\label{Res.2}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/causes.pdf}
	\caption{
		Causes of water governance regime shifts in the YRB.
		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the irrigated area, the green dot line).
		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line).
		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time. Red circles denote the reservoirs mainly for managing and regulating the whole basin.
		The size of each circle indicates the magnitude of its water storage capacity.
		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2). The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
	}
	\label{fig:Causes}
\end{figure*}

% 进一步挖掘IWGI变化的根本原因，
The underlying causes of changes in the IWGI are different in the two regime shifts.
% 灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
Changing water demands and supply were critical to the shift between P1 and P2.
% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2.
% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
Ensuing the P2, however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes}~A and B).
% 水分利用效率由P2变化到P3。
Then, the efficiency of water use changed obviously from P2 to P3.
Not only did irrigated areas continue to expand slowly during the P3 (Figure\ref{fig:Causes}~A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}~B).
Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}~A and Figure~\ref{fig:Causes}~B).
As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the P3 (Figure~\ref{fig:IWGI}A).

>>>>

% chktex-file 46
\subsection{Water governance regimes}\label{Res.1}

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/index.jpg}
	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: $1965 \sim 1978$, P2: $1979 \sim 2001$, and P3: $2002 \sim 2013$.
	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
	\textbf{B,} correlation of trends between the IWGI and the indicators.
	\textbf{C,} across three indicators, changing components of the IWGI, whose directions shifts between different regimes.
	}\label{fig:IWGI}
\end{figure*}

% 这一节主要展示IWGI的变化趋势和WUR的划分
Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
% 第一阶段
In the first period (P1, $1965 \sim 1978$), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
% 第二阶段
In the second period (P2, $1979 \sim 2001$), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.\
% 第三阶段
During the third period (P3, $1995 \sim 2013$), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
% Overall
Taken together, the overall features of the three aspects in different periods are relative to a directional change in the combination of three aspects (Figure~\ref{fig:IWGI}C).

\subsection{Causes of the regime shifts}\label{Res.2}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/causes.pdf}
	\caption{
		Causes of water governance regime shifts in the YRB.\
		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the irrigated area, the green dot line).
		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line).
		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time. Red circles denote the reservoirs mainly for managing and regulating the whole basin.
		The size of each circle indicates the magnitude of its water storage capacity.
		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colours denote signed by different state institutions, see \textit{Supporting Information} Table~S2). The light grey bars count official documents related to the YRB on a basinal scale (the Yellow River Events).
	}\label{fig:Causes}
\end{figure*}

% 进一步挖掘IWGI变化的根本原因，
The underlying causes of changes in the IWGI are different in the two regime shifts.
% 灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
Changing water demands and supply were critical to the shift between P1 and P2.
% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
As the dominant water demand during the P1, the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6~ha/yr$ (Figure\ref{fig:Causes}~A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{Supporting Information} Figure~S2). % todo 检查图引用
% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
Ensuing the P2, however, the expansion of irrigated areas slowed down, and industry and services gradually took off (Figure\ref{fig:Causes}~A and B).
% 水分利用效率由P2变化到P3。
Then, the efficiency of water use changed obviously from P2 to P3.
Not only did irrigated areas continue to expand slowly during the P3 (Figure\ref{fig:Causes}~A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}~B).
Because of increased efficiency, however, they both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}~A and Figure~\ref{fig:Causes}~B).
As a result, the differences between sectors and regions in water use reduced while the total water stress steadily remained high during the P3 (Figure~\ref{fig:IWGI}A).
